MSAD_PCA_Walkthrough

### 2017-01-28 Simulation_Vignette.Rmd
mspMonitor function written and partially documented, but tests fail somewhere in the faultDetect call. ERROR: observation %*% P : non-conformable arguments. However, this should not be the case, as the observations should be 1 * 9 row vectors and P is a 9 * 3 projection matrix. USE mspMonitor IN DEV ONLY.

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 2)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

@@

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 2)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

@@

## Test the Multi-State Monitoring function
```{r test_msad-pca}
# Create six observations with lags 0:2 included
laggedTestObs <- faults_ls$normal[10073:10080, -1]
laggedTestObs <- stats::lag(laggedTestObs, 0:-2)
laggedTestObs <- cbind(faults_ls$normal[10073:10080, 1], laggedTestObs)
laggedTestObs <- laggedTestObs[-(7:8),]
mspMonitor(observations = laggedTestObs[,-1],
           labelVector = laggedTestObs[,1],
           trainingSummary = results_ls$TrainingSpecs)
```
